% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

Never planning before to get here, until the opportunity came, I cannot express my happiness in words for one of the most worthwhile experiences in my life. While tackling the problems during a PhD, one may learn invariable lessons: from self-adjustment to facing the failures; from bitterness of being on the verge of hopelessness, to the beauty of getting the confidence and inclination to question all that is around, and seek out new ways of doing it. Most importantly, the lesson of learning to push yourself out of comfort zone to make progress.

Without a doubt, I would not be able to sit and write this acknowledgement today without many people throughout my life, who their presence and true friendship in a times of need have shed the light of beauty into my life. Although not being able to name all, I will never forget any of them.

I am and will always be deeply indebted to my PhD supervisor Prof. Hamid Aghvami, the head of the Centre for Telecommunication Research. I am deeply grateful for the guidance, encouragements and support he provided throughout my PhD.
A special thanks to Dr. Andrej Mihailovic who helped me greatly during my PhD research study. I have true appreciation for his valuable suggestions and insights and the collaborative works produced towards writing papers. He always had faith in me and supported me throughout my studies which I am very thankful for.


\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
